\documentclass{beamer}
\usetheme[pageofpages=of,% String used between the current page and the
                         % total page count.
          bullet=circle,% Use circles instead of squares for bullets.
          titleline=true,% Show a line below the frame title.
	  titlepagelogo=opensuse,
          alternativetitlepage=true,% Use the fancy title page.
          ]{Torino}

\setbeamerfont{title}{series=\bfseries,size=\LARGE}
\author{Michal Hru\v{s}eck\'{y}\newline {\small openSUSE Boosters}}
\title{Collaboration with universities}

\begin{document}

\begin{frame}[t,plain]
\titlepage
\end{frame}

\begin{frame}[t]
\frametitle{GSoC}
Few numbers:
\begin{itemize}
	\item 57 proposals
	\item 15 selected projects
	\item 13 successfully finished projects
\end{itemize}

\pause
\vspace{0.5cm}
Meaning:
\begin{itemize}
	\item many interesting topics around
	\item many volunteers to mentor students
	\item many students interested in working for openSUSE
\end{itemize}

{\(\Rightarrow\) students wants to work with us and we want to work with them}

\end{frame}

\begin{frame}[t]
\frametitle{What do we have?}
Skilled people with
\begin{itemize}
	\item experience
	\item knowledge
	\item crazy ideas
	\item long ToDo lists
	\item not enough time
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{What do universities have?}
Students
\begin{itemize}
	\item eager to learn new things
	\item wanting to prove themselves
	\item seeking help and guidance
	\item in need of topic for their thesis
	\item urge to code {\scriptsize (and party)}
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Cooperation?}
How can we help?
\begin{itemize}
	\item teach
	\item provide topics for thesis
	\item mentor open source project
\end{itemize}
\pause
\vspace{0.5cm}
What we will get?
\begin{itemize}
	\item raise awareness of open source
	\item new potential contributors
	\item implementation of parts of our ToDo lists
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{How can we do that?}
Little bit of my ideas:
\begin{itemize}
	\item find local universities and talk to them
	\item talk to people in communities and make them verbose
	\item create some web application
	\begin{itemize}
		\item gather people
		\item topics they can do presentations about
		\item projects and mentors
		\item provide means for feedback
		\item promote it heavily on universities
		\item teachers and students will pick the topics they are interested in
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{How can we do that?}
Your ideas:
\vspace{2cm}
\begin{center}
{\Huge Any ideas?}
\end{center}
\end{frame}

\sectionpage{Discusion}

\end{document}

